ShabbyPages: A Recipe for Repeatable, Synthetic, Modern Document Images

### 2023-02-07 paper/paper.tex
remove commented bibliography, trim denoising results table

\section{Introduction}
Supervised learning requires a collection of training data and accompanying ``labels'', which in the graphical modality are clean images, free of noise or other degradations.
ShabbyPages is a large dataset composed of 6202 clean/noisy pairs of images taken from 600 digital documents.
Information about the set's contents and its relation to other datasets are explored in the next section.
The noisy images were created from their clean origins by the application of a pipeline developed with the Augraphy library; the production of ShabbyPages is detailed in the third section, with all source code and input materials made openly available.
The final dataset is used to train several denoising models which are compared directly and whose prediction results are compared together in the final section.

@@

\begin{table}[]
    \centering
    \caption{Document image binarization performance of a NAFNet model trained and tested on ShabbyPages and NoisyOffice.}
    %\caption{Document image binarization performance between NoisyOffice-trained and ShabbyPages-trained NAFNet binarizing de    noisers on cross-validation task}
    \scalebox{0.9}{
    \begin{tabular}{lllll}
    \toprule
    \textbf{Training Set~~} & \textbf{Test Set} & \textbf{SSIM$\uparrow$~} & \textbf{RMSE$\downarrow$~} & \textbf{PSNR$\uparrow$} \\
        \midrule
        \textsf{ShabbyPages} & \textsf{ShabbyPages} & 0.926 & 2.99 & 39.3\\
        \textsf{NoisyOffice-sim} & \textsf{NoisyOffice-real~} & 0.987 & 3.80 & 36.7\\
        \textsf{ShabbyPages} & \textsf{NoisyOffice-real} & 0.947 & 3.20 & 38.1\\
        \textsf{NoisyOffice-sim} & \textsf{ShabbyPages} & 0.811 & 5.38 & 34.6\\
        \bottomrule
    \end{tabular}}
    \label{tab:binarization_results}
\end{table}

@@

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
 \bibliographystyle{splncs04}
 \bibliography{paper}

%\begin{thebibliography}{8}
%\bibitem{ref_Kaggle}
%  https://www.kaggle.com/datasets
%\bibitem{ref_HuggingFaceHub}
%  {https://huggingface.co/datasets}
%\bibitem{ref_RDCL2019}
%{Christian Clausner, RDCL2019 Competition Dataset (Recognition of Documents with Complex Layouts) (RDCL2019) ,1,ID:RDCL2019\_1,URL:https://tc11.cvc.uab.es/datasets/RDCL2019_1}
%
%\bibitem{ref_Tobacco800}
%{David Doermann, Tobacco 800 Dataset (Tobacco800) ,1,ID:Tobacco800_1,URL:https://tc11.cvc.uab.es/datasets/Tobacco800_1}
%
%\bibitem{ref_icdar}
%{Harold Mouchère, ICDAR 2019 Competition on Recognition of Handwritten Mathematical Expressions and Typeset Formula Detection (ICDAR2019-CROHME-TDF) ,1,ID:ICDAR2019-CROHME-TDF\_1,URL:https://tc11.cvc.uab.es/datasets/ICDAR2019-CROHME-TDF_1}
%
%\bibitem{ref_NoisyOffice}
%{Castro-Bleda, MJ.; España Boquera, S.; Pastor Pellicer, J.; Zamora Martínez, FJ. (2020). The NoisyOffice Database: A Corpus To Train Supervised Machine Learning Filters For Image Processing. The Computer Journal. 63(11):1658-1667. https://doi.org/10.1093/comjnl/bxz098}
%
%\bibitem{ref_RVL-CDIP}
%  @article{DBLP:journals/corr/HarleyUD15,
%  author    = {Adam W. Harley and
%               Alex Ufkes and
%               Konstantinos G. Derpanis},
%  title     = {Evaluation of Deep Convolutional Nets for Document Image Classification
%               and Retrieval},
%  journal   = {CoRR},
%  volume    = {abs/1502.07058},
%  year      = {2015},
%  url       = {http://arxiv.org/abs/1502.07058},
%  eprinttype = {arXiv},
%  eprint    = {1502.07058},
%  timestamp = {Mon, 13 Aug 2018 16:48:54 +0200},
%  biburl    = {https://dblp.org/rec/journals/corr/HarleyUD15.bib},
%  bibsource = {dblp computer science bibliography, https://dblp.org}
%}
%
%\bibitem{ref_NoisyOfficeDatabase}
%{F. Zamora-Martinez, S. España-Boquera and M. J. Castro-Bleda, Behaviour-based Clustering of Neural Networks applied to Document Enhancement, in: Computational and Ambient Intelligence, pages 144-151, Springer, 2007.}
%
%\bibitem{ref_UCIMLR}
%{Dua, D. and Graff, C. (2019). UCI Machine Learning Repository [http://archive.ics.uci.edu/ml]. Irvine, CA: University of California, School of Information and Computer Science.}
%
%\bibitem{ref_DocCreator}
%  {Journet Nicholas, Visani Muriel, Mansencal Boris, Van-Cuong Kieu, Billy Antoine, DocCreator: A New Software for Creating Synthetic Ground-Truthed Document Images. J. Imaging 2017, 3, 62.}
%\bibitem{ref_goldmann}
%  {Pau Riba, Anjan Dutta, Lutz Goldmann, Alicia Fornes, Oriol Ramos, Josep LLados: "Table Detection in Invoice Documents by Graph Neural Networks", ICDAR, 2019.}
%\bibitem{ref_zenodo}
%  {Layout Analysis Groundtruth for the RVL-CDIP Dataset. Goldmann, Lutz. 10.5281/zenodo.3257319}
%\bibitem{ref_tobacco800gt1}
%  {Guangyu Zhu, Yefeng Zheng, David Doermann,and Stefan Jaeger. Multi-scale Structural Saliency for Signature Detection. In Proc. IEEE Conf. Computer Vision and Pattern Recognition (CVPR 2007), pp. 1‐8, 2007.}
%\bibitem{ref_tobacco800gt2}
%  {Guangyu Zhu and David Doermann. Automatic Document Logo Detection. In Proc. 9th Int. Conf. Document Analysis and Recognition (ICDAR 2007), pp. 864‐868, 2007.}
%
%\bibitem{ref_NAFNet}
%  @misc{https://doi.org/10.48550/arxiv.2204.04676,
%  doi = {10.48550/ARXIV.2204.04676},
%  url = {https://arxiv.org/abs/2204.04676},
%  author = {Chen, Liangyu and Chu, Xiaojie and Zhang, Xiangyu and Sun, Jian},
%  keywords = {Computer Vision and Pattern Recognition (cs.CV), FOS: Computer and information sciences, FOS: Computer and information sciences},
%  title = {Simple Baselines for Image Restoration},
%  publisher = {arXiv},
%  year = {2022},
%  copyright = {arXiv.org perpetual, non-exclusive license}
%}
%
%
%\end{thebibliography}
\end{document}

>>>>

\section{Introduction}
%Supervised learning requires a collection of training data and accompanying ``labels'', which in the graphical modality are clean images, free of noise or other degradations.
%ShabbyPages is a large dataset composed of 6202 clean/noisy pairs of images taken from 600 digital documents.
%Information about the set's contents and its relation to other datasets are explored in the next section.
%The noisy images were created from their clean origins by the application of a pipeline developed with the Augraphy library; the production of ShabbyPages is detailed in the third section, with all source code and input materials made openly available.
%The final dataset is used to train several denoising models which are compared directly and whose prediction results are compared together in the final section.

Denoising is an important task in many document processing workflows, wherein unwanted artifacts introduced to a document image via noisy processes like scanning are removed.
The effectiveness of the denoising stage of document processing pipelines has implications for downstream tasks like optical character recognition (OCR) and layout parsing [need to cite].
Furthermore, recent work has found that supervised machine learning methods yield promising results at the denoising task [need to cite].
Therefore, it is critical to have access to large-scale, high-quality training and evaluation data for document denoising.

Prior work has introduced denoising and binarization datasets, but these are often small in scale, limited in the types of noise, or not diverse enough to train robust denoising models.
For instance, the DIBCO datasets are far too small for large-scale training; each DIBCO dataset ranges between 10-20 images total.
The NoisyOffice denoising dataset \cite{ref_NoisyOfficeDatabase} is small in scale (having \emph{n} training samples), and limited in the types of noise.
NoisyOffice consists of artificial wrinkles and stains, but these only scratch the surface with regards to the plethora of noise types that occur in the real world.
The DDI-100 corpus \cite{ddi-100-2019} is larger in scale than NoisyOffice and the DIBCO datasets, but is again limited in the amount of noise and diversity \cite{detection-masking-2022}.

In this paper, we introduce a new dataset designed for the document denoising task.
This new dataset, \emph{ShabbyPages}, is large-scale, having \emph{nnn} training and \emph{mmm} testing samples.
\emph{ShabbyPages} is more diverse than alternatives like NoisyOffice, as it contains documents from various language groups and contains documents with graphical elements like tables and figures.
We discuss \emph{ShabbyPages} in this paper, providing motivation and context for its creation.
We also demonstrate its utility by benchmarking document denoising models.

@@

\begin{table}[]
    \centering
    \caption{Document image binarization performance of a NAFNet model trained and tested on ShabbyPages and NoisyOffice.}
    %\caption{Document image binarization performance between NoisyOffice-trained and ShabbyPages-trained NAFNet binarizing de    noisers on cross-validation task}
    \scalebox{0.9}{
    \begin{tabular}{lll}
    \toprule
    \textbf{Training Set~~} & \textbf{Test Set} & \textbf{SSIM$\uparrow$~}\\
        \midrule
        \textsf{ShabbyPages} & \textsf{NoisyOffice-real} & 0.947\\
        \textsf{NoisyOffice-sim} & \textsf{ShabbyPages} & 0.811\\
        \bottomrule
    \end{tabular}}
    \label{tab:binarization_results}
\end{table}

@@

\bibliographystyle{splncs04}
\bibliography{paper}
\end{document}
